Distributed Version Control Systems

### 2010-05-16 paper.tex
Seccion de Architecture casi terminada

In a DVCS like Git, everybody has the full repository in their hard drives.
Since there is no central server, all the operations on the repository are done 
offline. This means that actions like commiting do not depend on having a 
network connection, since commits are made on your repository.

Changes can thus be shared between everyone passing changes between repositories, 
without the need of making those changes in a central repository.

% Explicaremos el principio de funcionamiento de la herramienta distribuida 
% y sus principales objetivos, contrastando el flujo de trabajo con el de un 
% sistema de control de versiones centralizado. Básicamente que cada uno tiene 
% su propio repositorio, que las versiones pueden ser infinitas (por más que 
% haya una(s) maestra(s)), que se puede trabajar offline, etc.

% -habria que agregar una imagen de muetsra

\subsection{More Atomical Commits}

In a centralized VCS, most of the time commits aren't done until you are sure that 
the change is well written and can be actually shared to everybody else, since the 
commit is going to be shared as soon as it's done. In a DVCS the nature of the commits 
is different, since commits are made in the local repository only. Therefore, they can be more atomic, 
because commits aren't huge changesets but can be logical, coherent and smaller changes.

Many little commits, if needed, can be grouped as a bigger, conceptual commit.
To do this in a centralized VCS, one would have to create a new branch of the source code, 
and then merge the branch back to the trunk. But creating and merging branches all the time is 
not effortless, and branches can be seen by everybody that has access to the repository, 
so this is not always done.

Doing logical commits allows you to do apply a technique called ``cherry-picking'', 
which consists of ``picking'' what changes you want to use in a version, and build 
a new version containing only those changes. This way the revision tree is seen as a 
series of \emph{changesets} or \emph{patches} instead of just a series of static versions
(this also makes commits easier).

%En el sistema distribuido, hay una diferencia conceptual con los sistemas 
%centralizados acerca de la naturaleza de un commit. Se tiende a hacer commits
%más atómicos y lógicos ya que el commit se hace en el repositorio propio, 
%entonces no hay preocupaciones como romper el build.

\subsection{Tagging and Branching}

%En un sistema distribuido, tener muchísimos branches es sencillo, de hecho 
%es más que sencillo, es "natural". Lo que permite un sistema distribuido es 
%no solo tener branches baratos sino también simplificar los merges.

Centralized VCS's like Subversion makes certain copies through history called tags. 
On Git we have more tools, with one of them you can have an arbitrary 
description attached in the tag. In fact, you can store the whole release announcements there. 
Moreover, as with the commit, the identity of who made the tag is stored and this identity 
can be securely verified if we add a cryptographically PGP sign to the tag.

\subsection{Merging}

Merge on Git between branches is greatly improved over SVN, because all the history of 
both branches is preserved over the merges.
When we make a merge we have two scenarios:
Fast-forward merge: we refer to this when the changes only was made on only one of the branches,
they are simply replayed on the other branch.
Three-way merge: When changes exists on both branches, they are merged and git will report any 
conflict and let you resolve them.

\subsection{Pushing and pulling}

% comentario via nps: cambié ``co-worker'' por ``peer'' porque es más neutral
When we want to share our work with the rest of the team we have two basic concepts, 
\emph{push} and \emph{pull}.
Push refers to taking all my changes and add them to the repository of another peer. 
But in practice we don't do this becouse we shouldn't make a push on a peer working copy, 
instead it, we push in a ``central repository'' where all the team make their pushes too, 
this logic is similar to traditional VCS, but we need to keep in mind that we could have a 
lot of ``central repositories'' for different parts of our project.
Pull is a composite action of ``fetch'' and ``merge'', fetching takes the changes from selected 
repository of a peer and copies them to a local repository, and 
then those changes are merged with the sourcecode of my local repository.
In the same way, another peer can pull on my working copy and get my code and 
changes without any problem.

@@

\subsection{Merging}
Merging on Git between branches is greatly improved over SVN, because all the history of 
both branches is preserved over the merges. %agregar citation

\subsection{Sharing changes}
If you work simply pulling and pushing against a central repository, those operations do look 
very much like the operations idea of check out and check in in a centralized VCS, 
but that's the only way of sharing changes in a centralized VCS.
In a DVCS, since every repository is a peer to each other, anyone can share their repository in 
read-only mode (via ssh, http, or simply sharing the directory) to let other people pull from them.

@@

\end{thebibliography}

>>>>

A DVCS has many features that makes it perfect for distributed and non-distributed developments. Almost every feature is based on the fact that DVCS is distributed instead of centralized and therefore if you work distributed then merges would happen on a regular basis and they should be as fast and easy as possible, providing developers with a whole new set of tools and relieve them almost completely from having to code according to the rules required to work with a centralized CVS like system.

\subsection{Distributed}
The idea behind being distributed means that no server has the full content of a repository but rather a clone of it with the changes that a particular developer has commited. This allows users to have their own clone on their own computer and work in a offline environment while being able to version their changes. It also makes the whole versioning system faster.

\subsection{Change-sets}
You could also create several other clones for every feature or bug that they want to develop and push those changes to another clone, a peer's repository for instance, and pull some changes from another peer to your local clone. To able to do this, a DVCS tracks change-sets instead of changes in individual files so that it can keep track of all the changes needed for a feature/bug to work.

\subsection{Patchs}
The idea of having several clones, one for each feature or bug might be problematic so instead of doing that, you could have all your changes on a single clone and then select which one of those changes you want to commit. You can even select which parts of a single file you want to commit and which ones you don't, then group those changes and commit them in a very atomic way.

\subsection{Flexibility}
If you need a centralized repository you could still use a DVCS and all it's features while pushing all the changes to a particular repository. This shows how flexible a DVCS is, to the point of being able to describe it as a super-set of a centralized CVS although in really it is not.

\subsection{Trust Based Security}
Security on DVCS is based on the "circle of trust" model which implies that you trust only on a very specific group of people and you only pull from those people which in turn trust in their own group of people and only pull from that other group of people. This creates a chain of trust so that even if you don't trust some one directly by scalating their changes you could end up having his code only after it has been reviewed by the people you really trust.

\subsection{Small, Coherent and Logical Commits}
Due to the fact that you can select very specific pieces of your code to build a commit you can make commits very small and atomic making the merging process more easy by selecting only those commits that won't break your code. This technique of only selecting the changes that you want is called ``cherry-picking'' and it has the advantage of using the revision tree as a 
series of \emph{changesets} or \emph{patches} instead of just a series of static versions. The distributed model enhances this by allowing to make commits whenever you want to your local copy without breaking anyone else's code. Many little commits can be grouped as a bigger, conceptual commit in the case that you need those changes to occur at the same time and not individually.

\subsection{Tagging and Branching}
Most DVCS allows the user to attach an arbitrary description the a tag so you can store the whole release announcements along with the tag of that version. Moreover, as with the commit, the identity of the user who made the tag is stored and can be securely verified by a cryptographical PGP signature that is embedded on the tag

\subsection{Merging}
The merging process has two possible scenarios:
\emph{Fast-forward merge:} The changes has been applied to only one of the branches and therefore those changes are replayed to the other branch automatically.
\emph{Three-way merge:} When changes exists on both branches, the DVCS tool will try to automatically merge them and if any conflict arises then it reports it to you and let you resolve them. 
The merging process\cite{svnmerging} between branches preserves all the history of 
both branches on many DVCS tools.

\subsection{Pushing and pulling}
When we want to share our work with the rest of the team we have two basic commands, 
\emph{push} and \emph{pull}.

\subsection{Pushing}
The push process refers to taking all the changes previously selected and adding them to the repository of another peer. In practice we usually don't do this because we shouldn't push changes to a peer's working copy of the repository so the push process is usually done agains a ``central repository'' where all the team make their pushes too. This logic is similar to centralized VCS, but we must keep in mind that we could have a lot of ``central repositories'' for different parts of our project or even for different parts of the team. Testing could have its own central repository, while development has another copy of it and changes could be pushed among them very easily.

\subsection{Pulling}
Pull is the opposite action of push and it is the combination of two other commands, ``fetch'' and ``merge''. The fetch command takes the changes from a peer's repository and copies them to the local repository. After that, the merge process combines the changes you've just downloaded with the ones on your local repository. You can do those two actions separately or altogether by using the ``pull'' command.

@@

@@

\bibitem{svnmerging}
\newblock \emph{ Git-SVN Crash Course}

\newblock \emph{http://git.or.cz/course/svn.html#merge}
\end{thebibliography}
